An New Search for Supernova Remnants in NGC\,6946

### 2019-01-09 ms.tex
Updates from ShareLaTeX

\begin{figure}
\plotone{rgb_10arcmin_no_regions.png}
\caption{An emission-line image of \gal, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left.  {\bf Frank to update} }
\end{figure}

>>>>

\begin{figure}
\plotone{NGC6946_rgb_coords.png}
\caption{An emission-line image of \gal, where R = \ha, G = \sii, and B = \oiii, taken from the 3.8m WIYN telescope at Kitt Peak.  Yellow circles indicate the positions of the ten historical SNe since 1917 (including SN\,2017eaw, which occurred subsequent to our observations). The dashed rectangle indicates the small region shown in detail in Fig.~\ref{fig_4_panel_detail}.  The field is 10\arcmin\ square. 
\label{fig_rgb_overview}}
\end{figure}
